An Empirical Study of Invasion and Resistance for Iterated Prisoner's Dilemma Strategies

### 2017-05-19 main.tex

To complement Figures~\ref{fig:ranks_v_size_invade} and~\ref{fig:ranks_v_size_resist}, \ref{fig:ranks_v_size_coexist} shows
the rank of each strategy based on \(x_{N/2}\).
Tables~\ref{tbl:ranks_v_size_invade},~\ref{tbl:ranks_v_size_resist}
and~\ref{tbl:ranks_v_size_coexist} show the same information for a selection of
strategies:

>>>>

To complement Figures~\ref{fig:ranks_v_size_invade} and~\ref{fig:ranks_v_size_resist}, Figure~\ref{fig:ranks_v_size_coexists} shows the rank of each strategy based on \(x_{N/2}\).
Tables~\ref{tbl:ranks_v_size_invade},~\ref{tbl:ranks_v_size_resist}
and~\ref{tbl:ranks_v_size_coexist} show the same information for a selection of
strategies:
